Covariate analysis of MSSM reprocessed counts (with CQN normalisation and covariates adjusted)

### 2017-12-21 code/Rmd/MSSM_REPROCESSED.Rmd
Minor fix in MSSM code to accommodate recent changes in individual ID issue.

# Github link
thisRepo <- getRepo(repository = "th1vairam/Brain_Reg_Net", ref="branch", refName='AMPAD_reprocessing')
thisFile <- getPermlink(repository = thisRepo, repositoryPath=paste0('code/Rmd/',thisFileName))
```
### Data download
#### Obtain count matrix and metadata from synapse.
```{r download.data}
# Get reprocessed sample counts for temporal cortex
COUNT_ID <- 'syn8691099';#'syn7994853';
ALL_USED_IDs <- COUNT_ID
COUNT <- read.table(synGet(COUNT_ID)@filePath, header=T, sep='\t', check.names = F, row.names = 1)

@@

# Get 90+ age
METADATA_AGE_ID = 'syn10156693'
ALL_USED_IDs[length(ALL_USED_IDs)+1] = METADATA_AGE_ID
METADATA_AGE <- read.table(synGet(METADATA_AGE_ID)@filePath, sep='\t', header=T) %>%
  dplyr::rename(individualIdentifier = BBid)

>>>>

# Github link
thisRepo <- getRepo(repository = "th1vairam/Brain_Reg_Net", ref="branch", refName='AMPAD_reprocessing')
thisFile <- getPermlink(repository = thisRepo, repositoryPath=paste0('code/Rmd/',thisFileName))
```
### Data download
#### Obtain count matrix and metadata from synapse.
```{r download.data}
# Get reprocessed sample counts for temporal cortex
COUNT_ID <- 'syn8691099';
ALL_USED_IDs <- COUNT_ID
COUNT <- read.table(synGet(COUNT_ID)@filePath, header=T, sep='\t', check.names = F, row.names = 1)

@@

# Get 90+ age
METADATA_AGE_ID = 'syn10156693'
ALL_USED_IDs[length(ALL_USED_IDs)+1] = METADATA_AGE_ID
METADATA_AGE <- read.table(synGet(METADATA_AGE_ID)@filePath, sep='\t', header=T)
